---
title: Analysis of conversion
author: 'Konstantin Shmirko'
date: '2021-04-20'
slug: analysis-of-conversion
categories: [R, conversion]
tags: []
---

Consider a typical task for the data analytics: some Internet portal for the sale of used cars decided to increase the conversion by changing the style and attractiveness of some user interface elements. The color of the button 'communicate with the seller' is changed. After that, AB testing was carried out in which a group of users saw a button in the old style, and the group B - in the new.

The task is to determine the change in conversion and evaluate its significance.


User statistics are given in the table.

| Result        | Case A | Case B |
|:--------------|-------:|-------:|
|Conversion     | 7339   | 6645   |
| No Conversion | 19843  | 16530  |


```{r echo=TRUE, warning=FALSE, cache=TRUE}

perm_fun <- function(x, n1, n2) {
  n <- n1 + n2
  idx_b <- sample(1:n, n1)
  idx_a <- setdiff(1:n, idx_b)
  mean_diff <- mean(x[idx_b]) - mean(x[idx_a]) 
  return(mean_diff)
}


obs_pct_diff<-100*(6645/23175-7339/27182)
conversion<-c(rep(0, 36373), rep(1, 13984))
perm_diffs <-rep(0, 1000)

for(i in 1:1000){
  perm_diffs[i] <- 100*perm_fun(conversion, 27182, 23175)
}

hist(perm_diffs, xlab='Random change in conversion', xlim = c(-1.8, 1.8), main = "")
abline(v = obs_pct_diff)
text(x=obs_pct_diff, y=180, labels = "Observed conversion", adj=1)
```

Based on the drawing, we see that the experimental change in conversion lies much to the right than the change of conversion due to random processes. Thus, we can conclude that the change in conversion is 1.67% - is a statistically significant and new button color is better than old one.

Conversion In our case, this is the ratio of the number of users who pressed the button to the total number of unique site visitors. Thus, the observed change in conversion in our AB test is the difference between conversion in the considered groups A and B.

Well, but how in this case, assess the significance? Let's consider two hypotheses - zero hypothesis sounds like 'the observed difference in conversion is random', while alternative - 'the difference observed in conversion is not random'.

Change of the conversion will be significant if it is greater than random conversion change.

Let's simulate a random process, in which among 50357 unique visitors conversion was in 13984 cases. That is, we create a vector of length 50357, in which the 36373 elements are zero, and 13984 are equal to 1. Now we randomly form two vectors A and B of length 27182 and  23175 consequently  many times (e.g. 1000). 

In each vector, we will consider the ratio of the number of units to the sample size and find the difference between themselves. $\delta=\frac{count(A==1)}{length(A)}-\frac{count(B==1)}{length(B)}$

At each iteration, the change in the $\delta$  was saved in the vector and later used to build the histogram.


## Alternative approach ##

What we have done above is called bootstrapping, we simulate statistical experiment many times and then give the explanation through analysis of the result.

But this technique becomes available only in computer era. 

We also can get same results using z-test (for large sample size) of Fisher Exact probability test otherwise. In this case we have following hypotheses

1. $H_0: p_A=p_B$
2. $H_0: p_A \le p_B$
3. $H_0: p_A \ge p_B$

and corresponding alternative hypotheses are:

1. $H_a: p_A \ne p_B$
2. $H_0: p_A \gt p_B$
3. $H_0: p_A \lt p_B$

The test ststistics can be calculated as follows:

$$
  z=\frac{p_A-p_B}{\sqrt{pq/n_A - pq/n_B}}
$$
where 

* $p_A$ is the proportion observed in group A with size $n_A$;
* $p_B$  is the proportion observed in group B with size $n_B$;
* $p$ and $q$ are the overall proportions.

The results interpretation:

- if $|z|\lt 1.96$, then the difference is not significant at $5\%$
- if $|z|\ge 1.96$, then the difference is significant at $5\%$

The significance level (p-value) corresponding to the z-statistic can be read in the z-table. We’ll see how to compute it in R.


this test can be done by means of R using `prop.test` function.

`
prop.test(x, n, p = NULL, alternative = "two.sided",
          correct = TRUE)
`

where

- x: a vector of counts of successes
- n: a vector of count trials
- alternative: a character string specifying the alternative hypothesis
- correct: a logical indicating whether Yates’ continuity correction should be applied where possible


We want to know, whether the obtained conversions are the same in the two groups of individuals?

``` {r echo=TRUE, warning=FALSE, cache=TRUE}

prop.test(x=c(7339,6645), n=c(27182, 23175))

```


The p-value of the test is $3.05\cdot10^{-5}$, which is less than the significance level alpha = 0.05. We can conclude that the proportion of smokers is significantly different in the two groups with a p-value = $3.05\cdot10^{-5}$.



